Monte Carlo and bootstrap for ALL parameters with tables

### 2024-08-16 All_tables.Rmd
Better tables and bigger test

---
title: "Monte Carlo and bootstrap for ALL parameters with tables"
output: pdf_document
date: "2024-08-02"
---

@@

```{r}
# The table itself
print(tab_real)
```

@@

```{r}
B0 <- 50
```

@@

```{r}
B1 <- 100
B2 <- 50
```

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
# The table itself
print(tab_ci)
```

@@

```{r}
# The table itself
print(tab_var)
```

>>>>

---
title: "Monte Carlo and bootstrap for ALL parameters with tables"
output: pdf_document
date: "2024-08-16"
---

@@

```{r}
# The table itself
tab_real
```

@@

```{r}
B0 <- 1000
```

@@

```{r}
B1 <- 200
B2 <- 100
```

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\hline"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
# The table itself
tab_ci
```

@@

```{r}
# The table itself
tab_var
```
